Examples Compendium

### 2021-02-14 draft.tex
just stylin
added tablaux equations to examples
long butt todo list
stashing conflicting local changes
moved some stuff around and added to todo
some abstracts some notes following sat mtg some other

\documentclass{article}
\usepackage{basic}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
% & , Joel Kamnitzer?
\author{Roger Bai, Anne Dranowski} 
\date{October 2020}

@@

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
        %L\otimes\CC[t^{-1}] 
        L \otimes_{\CC[t]} \CC\xt[t-s] 
        &\in \Gr^{\lambda_2} \text{ and } \\
        % L\otimes\CC[(s-t)^{-1}] 
        L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
        L \otimes_{\C[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
    \end{split}
\end{equation}

@@

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1[[t^{-1}]].
\]
\end{proof}

@@

>>>>

\documentclass{article}
\usepackage{basic}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
\date{October 2020}

@@

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
        %L\otimes\CC[t^{-1}] 
        L \otimes_{\CC[t]} \CC\xt[t-s] 
        &\in \Gr^{\lambda_2} \text{ and } \\
        % L\otimes\CC[(s-t)^{-1}] 
        L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
        L \otimes_{\CC[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
    \end{split}
\end{equation}

@@

In Anderson and Kogan conjectured in \cite{anderson2005algebra} \acom{or earlier?} that those MV polynomials which are cluster monomials for a Fomin--Zelevinsky cluster algebra structure on $\CC[N]$ are naturally expressible as determinants\dots
and they conjecture a formula for many of them.

It's not clear how this work helps/relates to AK/their conjectures.

The generalized MVy is interesting in its own right.

Computing fusion still hard but at least boiled down to linear algebra. Cf.\ fusion product as it appears in BD, FL, MV, AK, BFM.

\begin{quotation}
However, we make crucial use of an idea of Drinfeld, going back to around 1990. He discovered an elegant way of obtaining the commutativity constraint by interpreting the convolution product of sheaves as a ``fusion'' product.
\end{quotation}

Exchange relations only work on cluster modules where one is a mutation of the other (i.e.\ those corresponding to cluster monomials which are related by mutation). Of course this gives me everything. Up to $A_4$ as in type $A_5$ there exist indecomposable modules which are not cluster, so exchange relations do not apply. The hope (conjecture) is that this paper gives a way to compute on such modules. Cf.\ counterexample satisfying $\barD(c_Y) = \barD(b_Z) + 2\barD(b)$, where $b$ is (possibly) cluster, and suggesting that $c_Y = b_Z + 2b$.

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1[[t^{-1}]].
\]
\end{proof}

@@

\begin{conjecture}
    Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu_2$. 
\end{conjecture}

\bibliographystyle{alpha}
\bibliography{mvybd}

### 2021-02-14 examples.tex
typo ish
Updates from Overleaf
fixed comment example environment intersection error
long butt todo list
some abstracts some notes following sat mtg some other

Finally, we guess that the fusion $2\alpha_1 \ast 2\alpha_2$ is encoded by the tableau equation 
\[
\young(22) \ast \young(11,33) = \young(1122,33) + \young(1123,23) + \young(1133,22)     
\]
Remains to check this and make sense of the middle term.

@@

Note that these ideals correspond to expected tableaux as follows.
\begin{align}
\young(22) \ast \young(11,33) &= \young(1122,33) + {\color{red}2?}\young(1123,23) + \young(1133,22)  \\
  &= (A_4, A_5) + {\color{red}2?}(A_0,A_4) + (A_0, A_1) \\
  &= (20,2) + {\color{red}2?}(11,1) + (02,0) \\
  &= (11\to 22) + {\color{red}2?}((1\to (1\leftarrow 2))\to 2) + (11\leftarrow 22) \\ 
  &= (xy-z)^2 + 2(xy-z)z + z^2
\end{align} 
\begin{question}
    How do we tell from the tableaux that an ideal is occuring with multiplicity? 
\end{question}

@@

\[
A-s = \left[\begin{BMAT}(e){cccccc:cccc:cc}{cccccc:cccc:cc}
    -s & 1 & & & & & & & & & & \\
    & -s & 1 & & & & & & & & & \\
    & & -s & 1 & & & & & & & & \\
    & & & -s & 1 & & & & & & & \\
    & & & & -s & 1 & & & & & & \\
    & & & & -s^2 & s & 0 & 0 & a_3 & a_4 & b_1 & b_2 \\
    & & & & & & -s & 1 & & & & \\
    & & & & & & & -s & 1 & & & \\
    & & & & & & & & -s & 1 & & \\
    & & & & & & & & -s^2 & s & c_1 & c_2 \\
    & & & & & & & & & & -s & 1 \\
    & & & & & & & & & & & -s 
\end{BMAT}\right]
\]
\end{comment}
\end{example}

@@

Take 2: Let's try different weights.
\[
\begin{aligned}
    \mu_1 &= (1,1,0) & \lambda_1 &= (2,0,0) \\
    \mu_2 &= (1,1,1) & \lambda_2 &= (2,1,0) \\
    \mu &= (2,2,1) & \lambda &= (4,1,0)
\end{aligned}    
\]
and 
\[
\tau(1,0,0) = \young(12) \qquad \tau(1,0,1) = \young(12,3) \quad \tau(0,1,0) = \young(13,2)    
\]
Then 
\[
A = \left[\begin{BMAT}(e){cc;cc;c}{cc;cc;c} 
    0 & 1 & 0 & 0 & 0\\
    0 & s & A_0 & A_1 & A_2\\
    0 & 0 & 0 & 1 & 0\\
    0 & 0 & 0 & s & A_3\\
    0 & 0 & 0 & 0 & s
    \end{BMAT}\right]
\]
We have $E_0 \cap \CC^2 = \Sp(e_1)$, $E_s \cap \CC^2 = \Sp(e_1 + se_2)$. Next $E_0 \cap \CC^4$ is spanned by a 2-cycle generated by $-\frac{A_0} s e_2 + e_3$ and $E_s \cap \CC^4$ is spanned by a 2-cycle generated by 
$$
\frac{s}{A_1 + \frac{A_0}{s}}e_4 + \frac{1}{A_1 + \frac{A_0}{s}} e_3 - \frac 1 s e_1 
$$ 
or the additional 1-cycle $e_4 - \frac{A_1}{A_0} e_3$ assuming $A_0 + sA_1 = 0$. 
Finally $E_s$ is spanned by an additional 1-cycle 
$$
e_5 - \frac{A_2}{A_1 + \frac{A_0}{s}} e_4 + \frac 1 s \frac{A_2}{A_1 + \frac{A_0}{s}}e_3 
$$
assuming $A_3 = 0$.
% and $A_2 = 0$?? 
Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$.
% and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$??
This gives us 
\[
    \young(12) \ast \young(12,3) = (A_3) \qquad % A_2, 
    \young(12) \ast \young(13,2) = (A_0 + sA_1) \to (A_0) %  , A_3
\]  
Does it agree with what is expected on the module/cluster side? 
\[
S_1 \ast (1\to 2) = S_1 \oplus (1 \to 2) \qquad S_1 \ast (1\leftarrow 2) = S_1 \oplus (1 \leftarrow 2)
\]
The MV cycle of $\young(12)$ is a $\PP^1$: via MVy it has an open subset comprised of matrices 
\[
    \left[\begin{BMAT}(e){c;c}{c;c} 
        0 & A_0\\
        0 & 0
        \end{BMAT}\right] : A_0\ne 0
\]
The MV cycles of the other two tableaux are made up of matrices of the form 
\[
    \left[\begin{BMAT}(e){c;c;c}{c;c;c} 
        0 & A_0 & A_1\\
        0 & 0 & A_2\\
        0 & 0 & 0
        \end{BMAT}\right] : 
        \begin{cases}
            A_0 \ne 0 \text{ and } A_2 = 0 & \tau = \young(12,3) \\
            A_0 = 0 \text{ and } A_2 \ne 0 & \tau = \young(13,2)
        \end{cases} 
\] both $\CC^2$'s. \acom{How do the coordinates relate?}
% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$. The new 1-cycle must be $\{e_4\}$. \acom{Why?} Hence our first equation: $A_0 = 0$. As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$ 
% TODO: Make a table 
% 
% The zero eigenspace of $A$ conforms to the shape 
%     \[
%     \lambda_1 = \yng(3,1,1)    
%     \] 
%     is made of three cycles
%     \begin{align*}
%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
%         e_4 & \\
%         e_7 & 
%     \end{align*}
%     while the $s$-eigenspace confirming to the shape 
%     \[
%     \lambda_2 = \yng(2,1)    
%     \]
%     is made of the two cycles 
%     \begin{align*}
%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
%         e_4 + s e_5 + s^2 e_6 & 
%     \end{align*}
%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}
\newpage
\begin{example}[Roger]
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.

@@

\begin{example}[Above example redone]
    In $\CC[A_0..A_6]$ where 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c} 
            0 & 1 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
            0 & 0 & 0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & 0 & s & A_4 & A_5\\
            0 & 0 & 0 & 0 & 0 & s & A_6\\
            0 & 0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    
    \]
    we have 
    $$
    \begin{aligned}
        \young(12)*\young(11,23,4) &= ({\color{blue}A_6,A_2A_5-A_3A_4},A_1A_4 + A_2s,A_1s + A_0) \\
        &= (A_6,A_2A_5 - A_3A_4, A_1A_4,A_0) \text{ at } s = 0 \\
        &= (A_0,A_4,A_5,A_6) \sqcup (A_0,A_1,A_6,A_2A_5 - A_3 A_4) \sqcup (A_0,A_2,A_4,A_6)
    \end{aligned}
    $$ 
    while 
    $$
    \begin{aligned}
        \young(12)*\young(11,24,3) &= ({\color{blue}sA_0A_5 + (1 + s^2)A_1A_5+sA_3},A_2,A_4,A_1s + A_0) \\
        &= (A_1A_5,A_2,A_4,A_0) \text{ at } s = 0 \\
        &= (A_0,A_2,A_4,A_5) \sqcup (A_0,A_1,A_2,A_4) 
    \end{aligned} 
    $$
    Cycles are 
    \[
    \frac{A_0}{s^2}e_2 + e_4 \xrightarrow{A} e_1    
    \]
    and, in the $\young(11,23)$ case, 
    \[
    \begin{aligned}
        e_2 + 2s e_3 \xrightarrow{A-s} e_1 + se_2 + s^2 e_3 \\
        (sA_4 e_4 + (1 + s^2)A_4 e_5 + se_6)/(sA_4) \xrightarrow{A-s} (e_4 + se_5)/s 
    \end{aligned}    
    \]
    while in the $\young(11,2,3)$ case,
    \[
        \begin{aligned}
      e_6 \xrightarrow{A-s} 0 \\
      e_4 + (1/s + s) e_5 + (1/A_5) e_7 \xrightarrow{A-s} (1/s)e_4 + e_5 + \ast e_6   
        \end{aligned}
    \]
\end{example}
\end{document}

>>>>

Finally, we guess that the fusion $2\alpha_1 \ast 2\alpha_2$ is encoded by the tableau equation 
\[
\young(22) \ast \young(11,33) = \young(1122,33) + \young(1123,23) + \young(1133,22)     
\]
This is checked below.

@@

Note that these ideals correspond to expected tableaux as follows.
\begin{align}
\young(22) \ast \young(11,33) &= \young(1122,33) + {\color{red}2?}\young(1123,23) + \young(1133,22)  \\
  &= (A_4, A_5) + {\color{red}2?}(A_0,A_4) + (A_0, A_1) \\
  &= (20,2) + {\color{red}2?}(11,1) + (02,0) \\
  &= (11\to 22) + {\color{red}2?}((1\to (1\leftarrow 2))\to 2) + (11\leftarrow 22) \\ 
  &= (xy-z)^2 + 2(xy-z)z + z^2
\end{align} 
\begin{question}
    How do we tell from the tableaux that an ideal is occuring with multiplicity? 
\end{question}
\end{example}

@@

\[
A-s = \left[\begin{BMAT}(e){cccccc:cccc:cc}{cccccc:cccc:cc}
    -s & 1 & & & & & & & & & & \\
    & -s & 1 & & & & & & & & & \\
    & & -s & 1 & & & & & & & & \\
    & & & -s & 1 & & & & & & & \\
    & & & & -s & 1 & & & & & & \\
    & & & & -s^2 & s & 0 & 0 & a_3 & a_4 & b_1 & b_2 \\
    & & & & & & -s & 1 & & & & \\
    & & & & & & & -s & 1 & & & \\
    & & & & & & & & -s & 1 & & \\
    & & & & & & & & -s^2 & s & c_1 & c_2 \\
    & & & & & & & & & & -s & 1 \\
    & & & & & & & & & & & -s 
\end{BMAT}\right]
\]
\end{comment}

@@

Take 2: Let's try different weights.
\[
\begin{aligned}
    \mu_1 &= (1,1,0) & \lambda_1 &= (2,0,0) \\
    \mu_2 &= (1,1,1) & \lambda_2 &= (2,1,0) \\
    \mu &= (2,2,1) & \lambda &= (4,1,0)
\end{aligned}    
\]
and 
\[
\tau(1,0,0) = \young(12) \qquad \tau(1,0,1) = \young(12,3) \quad \tau(0,1,0) = \young(13,2)    
\]
Then 
\[
A = \left[\begin{BMAT}(e){cc;cc;c}{cc;cc;c} 
    0 & 1 & 0 & 0 & 0\\
    0 & s & A_0 & A_1 & A_2\\
    0 & 0 & 0 & 1 & 0\\
    0 & 0 & 0 & s & A_3\\
    0 & 0 & 0 & 0 & s
    \end{BMAT}\right]
\]
We have $E_0 \cap \CC^2 = \Sp(e_1)$, $E_s \cap \CC^2 = \Sp(e_1 + se_2)$. Next $E_0 \cap \CC^4$ is spanned by a 2-cycle generated by $-\frac{A_0} s e_2 + e_3$ and $E_s \cap \CC^4$ is spanned by a 2-cycle generated by 
$$
\frac{s}{A_1 + \frac{A_0}{s}}e_4 + \frac{1}{A_1 + \frac{A_0}{s}} e_3 - \frac 1 s e_1 
$$ 
or the additional 1-cycle $e_4 - \frac{A_1}{A_0} e_3$ assuming $A_0 + sA_1 = 0$. 
Finally $E_s$ is spanned by an additional 1-cycle 
$$
e_5 - \frac{A_2}{A_1 + \frac{A_0}{s}} e_4 + \frac 1 s \frac{A_2}{A_1 + \frac{A_0}{s}}e_3 
$$
assuming $A_3 = 0$.
% and $A_2 = 0$?? 
Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $-\frac{1}{s} e_1 + \frac s {A_2} e_5$.
% and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$??
This gives us 
\[
    \young(12) \ast \young(12,3) = (A_3) \qquad % A_2, 
    \young(12) \ast \young(13,2) = (A_0 + sA_1) \to (A_0) %  , A_3
\]  
Does it agree with what is expected on the module/cluster side? 
\[
S_1 \ast (1\to 2) = S_1 \oplus (1 \to 2) \qquad S_1 \ast (1\leftarrow 2) = S_1 \oplus (1 \leftarrow 2)
\]
The MV cycle of $\young(12)$ is a $\PP^1$: via MVy it has an open subset comprised of matrices 
\[
    \left[\begin{BMAT}(e){c;c}{c;c} 
        0 & A_0\\
        0 & 0
        \end{BMAT}\right] : A_0\ne 0
\]
The MV cycles of the other two tableaux are made up of matrices of the form 
\[
    \left[\begin{BMAT}(e){c;c;c}{c;c;c} 
        0 & A_0 & A_1\\
        0 & 0 & A_2\\
        0 & 0 & 0
        \end{BMAT}\right] : 
        \begin{cases}
            A_0 \ne 0 \text{ and } A_2 = 0 & \tau = \young(12,3) \\
            A_0 = 0 \text{ and } A_2 \ne 0 & \tau = \young(13,2)
        \end{cases} 
\] both $\CC^2$'s. \acom{How do the coordinates relate?}
% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$. The new 1-cycle must be $\{e_4\}$. \acom{Why?} Hence our first equation: $A_0 = 0$. As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$ 
% TODO: Make a table 
% 
% The zero eigenspace of $A$ conforms to the shape 
%     \[
%     \lambda_1 = \yng(3,1,1)    
%     \] 
%     is made of three cycles
%     \begin{align*}
%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
%         e_4 & \\
%         e_7 & 
%     \end{align*}
%     while the $s$-eigenspace confirming to the shape 
%     \[
%     \lambda_2 = \yng(2,1)    
%     \]
%     is made of the two cycles 
%     \begin{align*}
%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
%         e_4 + s e_5 + s^2 e_6 & 
%     \end{align*}
%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}
\newpage
\begin{example}[Roger]
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (2,1,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.

@@

\begin{example}[Above example redone]
    In $\CC[A_0..A_6]$ where 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c} 
            0 & 1 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_0 & A_1 & A_2 & A_3\\
            0 & 0 & 0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & 0 & s & A_4 & A_5\\
            0 & 0 & 0 & 0 & 0 & s & A_6\\
            0 & 0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    
    \]
    we have 
    $$
    \begin{aligned}
        \young(12)*\young(11,23,4) &= ({\color{blue}A_6,A_2A_5-A_3A_4},A_1A_4 + A_2s,A_1s + A_0) \\
        &= (A_6,A_2A_5 - A_3A_4, A_1A_4,A_0) \text{ at } s = 0 \\
        &= (A_0,A_4,A_5,A_6) \sqcup (A_0,A_1,A_6,A_2A_5 - A_3 A_4) \sqcup (A_0,A_2,A_4,A_6)
    \end{aligned}
    $$ 
    while 
    $$
    \begin{aligned}
        \young(12)*\young(11,24,3) &= ({\color{blue}sA_0A_5 + (1 + s^2)A_1A_5+sA_3},A_2,A_4,A_1s + A_0) \\
        &= (A_1A_5,A_2,A_4,A_0) \text{ at } s = 0 \\
        &= (A_0,A_2,A_4,A_5) \sqcup (A_0,A_1,A_2,A_4) 
    \end{aligned} 
    $$
    Cycles are 
    \[
    \frac{A_0}{s^2}e_2 + e_4 \xrightarrow{A} e_1    
    \]
    and, in the $\young(11,23)$ case, 
    \[
    \begin{aligned}
        e_2 + 2s e_3 \xrightarrow{A-s} e_1 + se_2 + s^2 e_3 \\
        (sA_4 e_4 + (1 + s^2)A_4 e_5 + se_6)/(sA_4) \xrightarrow{A-s} (e_4 + se_5)/s 
    \end{aligned}    
    \]
    while in the $\young(11,2,3)$ case,
    \[
        \begin{aligned}
      e_6 \xrightarrow{A-s} 0 \\
      e_4 + (1/s + s) e_5 + (1/A_5) e_7 \xrightarrow{A-s} (1/s)e_4 + e_5 + \ast e_6   
        \end{aligned}
    \]
\end{example}
\begin{example}
% weight a_1 + a_2 + a_3 = 1 0 0 -1
% can translate 
% 1->2<-3 * 1<-2->3 = S_1 \oplus P_2 \oplus S_3 + P_1 \oplus P_3
% 100,01,0 * 010,00,1 = 110,01,1 will correspond to S_1 \oplus P_2 \oplus S_3 module?
% 
% M_1 * M_2 = \sum M_\alpha 
% Pol(M_1) + Pol(M_2) = \cup Pol(M_\alpha) and all \alpha's are needed.. in all the A_3 exchange relations, not in this example

Try the following tableaux:
\[
1\to 2 \leftarrow 3 = \young(2,4) \qquad 1\leftarrow 2 \to 3 = \young(13,2,4)
\]
which won't work because $\mu_1 + \mu_2$ is not dominant. Can try anyway to see what fails.

Next best guess:
\[
1\to 2\leftarrow 3 = \young(12,24,3) 
\]

Question: can we do better? 
\end{example}

\section{\today}

\begin{example}
    Let $G = \SL_3(\CC)$ with the standard choices of $B$, $T$, and $N$. Then $\CC[N] = \CC[x,y,z]$ where 
    \begin{equation}
        \begin{bmatrix}
            1 & x & z \\
              & 1 & y \\
              &   & 1 
        \end{bmatrix}
    \end{equation}
    and the unique biperfect basis (also cluster basis in that it's generated by cluster monomials) is 
    \begin{equation}
        \{x^a z^b (xy-z)^c \}\cup \{y^a z^b (xy-z)^c \}
    \end{equation}
    where $a,b,c$ are non-negative integers.
\end{example}

\end{document}
